---
title: "Restless Bandits"
author: "Chris Harris, Dr. Florian Kutzner"
date: "Last edited: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: show
---

```{r setup, include=FALSE}

### Setup----

# Load dependencies
if (!require(needs)) {install.packages("needs"); library(needs)}
needs(dplyr, ggplot2, here, kableExtra, magrittr, stringr, plotly)
prioritize(dplyr)

### Functions----
source(here("Auxiliary/match_handler.R"))
source(here("Auxiliary/sim_handler.R"))
source(here("Auxiliary/determinechoice.R"))
source(here("Auxiliary/helpers.R"))
# Strategies
source(here("Strategies/positivist.R"))
source(here("Strategies/constructivist.R"))
source(here("Strategies/guessing.R"))
source(here("Strategies/omniscient.R"))

### Constants----
# Set up sine curves
x <- seq(0,pi*2*5,by = .1) # Trials
var <- 2 # Amplitude of sine curve
range <- max(max(abs(.2 * x + var * sin(x))),max(abs(-.2 * x + var * sin(x))))

# Positive
CURVE_A_pos <- (0.2 * x + var * sin(x)) / (2 * range) + .5 # Sine curve for option A
CURVE_B_pos <- (0.2 * x + var * sin(x + pi)) / (2 * range) + .5 # Sine curve for option B
# Neutral
CURVE_A_neu <- (var * sin(x)) / (2 * range) + .5 # Sine curve for option A
CURVE_B_neu <- (var * sin(x + pi)) / (2 * range) + .5 # Sine curve for option B
# Negative
CURVE_A_neg <- (-0.2 * x + var * sin(x)) / (2 * range) + .5 # Sine curve for option A
CURVE_B_neg <- (-0.2 * x + var * sin(x + pi))/(2 * range) + .5 # Sine curve for option B

# Create practice dataset
experienced <- rbind(rep("wA", 36),
            rep("lA", 36),
            rep(c("lA", "lB"), 18),
            rep(c("wA", "wB"), 18),
            rep(c("wA", "lA", "wB", "lB"), 9),
            rep(c("wA", "wA", "lB"), 12),
            rep(c("lB", "wB", "lB", "wA"), 9)) %>%
  as_tibble
constructed <- matrix(nrow = nrow(experienced),
                      ncol = ncol(experienced)) %>%
  data.frame() %>%
  transmute_all(.funs = funs(as.character(.))) %>%
  as_tibble()

memory <- list(experienced, constructed)
rm(experienced, constructed)
```

<!-- Style definitions -->
<style type="text/css">
h1.title {

  text-align: center;
}
h4.author {

  text-align: center;
}
h4.date {

  text-align: center;
}
</style>

<!-- Beginn body -->

#  {.tabset .tabset-fade}

## Summary

Journal: Memory & Cognition?  
Narrative: We investigate cyclicity, life is often cyclic, never before investigated only ever stationary or with trends.  
Strategies:  
Positivist - Juslin    
Constructivist - Juslin  
Both use windows as memory boundary - Kareev  
What do people do? What should they be doing?  
Always the why! Why are some strategies good, some poor?  
Discussion: Either people are reasonably good with cyclicity or our theoretical toolbox of strategies is incomplete.

<p>&nbsp;</p>
<p>&nbsp;</p>

Run everything as window strategies, either with or without constructed memory. Window sizes range from 1 to the max window size currently defined -> "growing windows". The max windows will range from 1 (WSLS) to all previous trials. However, to save time we will likely cut some corners, e.g. win_max = 1 - 14, 20, 40, ... all ("maximal window"). 


## Examples

Here are some small-scale examples of how the code works. The functional programming approach allows me to introduce a strategy, test it in isolation, and then use it both for simulating and for matching.  

Here are some examples that match expectations to behavior. This is done by taking each trial and assessing the expected outcome. Afterwards, a simple match to the actually taken choice provides a matching index.  

```{r Examples, results='asis', echo=FALSE}
match_handler(memory, "positivist", 1) %>%
  knitr::kable(caption = "Window, size 1") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
match_handler(memory, "positivist", 5) %>%
  knitr::kable(caption = "Window, size 5") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")

match_handler(memory, "constructivist", 1) %>%
  knitr::kable(caption = "Constructivist, size 1") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
match_handler(memory, "constructivist", 5) %>%
  knitr::kable(caption = "Constructivist, size 5") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")

match_handler(memory, "omniscient", "neutral") %>%
  knitr::kable(caption = "Omniscient, neutral") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
match_handler(memory, "omniscient", "neutral") %>%
  knitr::kable(caption = "Omniscient, negative") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")

match_handler(memory, "guessing") %>%
  knitr::kable(caption = "Guessing") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

```{r Examples2, results='asis', echo=FALSE}
matching_index <- vector(mode = "integer", length = 14)
for (i in 1:14) {
  matching_index[i] <- match_handler(memory, "positivist", i) %>%
    matching(memory[[1]], .) %>%
    mean
}

tibble(x = 1:14,
       y = matching_index) %>%
  ggplot(aes(x, y)) +
  geom_point() +
  scale_x_discrete(limits = 1:14) +
  labs(x = "Window size",
       y = "Mean guesses",
       title = "Mean number of guesses for positivist strategy") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()
```

Here are some examples that simulate a strategy. All guesses are resolved as a random selection of either choice. w/l stand for win or lose with the respectively chosen option.

```{r Examples3, results='asis', echo=FALSE}
sim_handler(strategy = "positivist",
            environment = "neutral",
            strat_var = 1,
            size = c(7, 12)) %>%
  knitr::kable(caption = "Positivist, neutral, window size 1") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
sim_handler(strategy = "constructivist",
            environment = "neutral",
            strat_var = 1,
            size = c(7, 12)) %>%
  knitr::kable(caption = "Constructivist, neutral, window size 1") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
sim_handler(strategy = "omniscient",
            environment = "positive",
            strat_var = 1,
            size = c(7, 12)) %>%
  knitr::kable(caption = "Omniscient, positive") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Finally, it is worth keeping track of the number of guesses that each study requires. A variation of the simulation handler counts guesses, which we can then plot (jittered):

```{r Examples4}
## Number of guesses
sequ <- seq(1, 9, 1)

# Positivist
df <- nr_guesses_per_strat("constructivist",
                           seq = sequ,
                           dims = c(100, 120))
df %>%
  ggplot(aes(x = sequence,
             y = guess_no,
             color = condition)) +
  geom_jitter() +
  scale_x_discrete(limits = sequ) +
  labs(x = "Window size",
     y = "Number of guesses",
     title = "Window strategy") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()

# Constructivist
df <- nr_guesses_per_strat("constructivist")
df %>%
  ggplot(aes(x = sequence,
             y = guess_no,
             color = condition)) +
  geom_jitter() +
  scale_x_discrete(limits = sequ) +
  labs(x = "Window size",
     y = "Number of guesses",
     title = "Constructivist strategy") +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()
```

## Code {.tabset .tabset-fade}

### Handlers {.tabset .tabset-fade}
The master script can call two main handlers depending on whether the goal is to simulate a strategy or to match to an existing behavior data set. The simulation handler has two versions, one that counts guesses and one that does not. Basically, without guesses is easier to program and always my intermediate step.  

#### The simulation handler:

This function runs the simulation and returns the expected choices
```{r Simulation Handler, eval=FALSE}
# Main handler of simulation runs
sim_handler <- function(strategy, environment, strat_var = NA, size) {
  # List to store expected choices
  df_sim <- matrix(nrow = size[1], ncol = size[2]) %>%
    as_tibble()
  df_const <- df_sim
  ml <- list(df_sim, df_const)
  rm(df_sim, df_const)
  # Determine outcome probabilities
  if (environment == "positive") {
    probabilities <- tibble(acurve = CURVE_A_pos, bcurve = CURVE_B_pos)
  } else if (environment == "neutral") {
    probabilities <- tibble(acurve = CURVE_A_neu, bcurve = CURVE_B_neu)
  } else {
    probabilities <- tibble(acurve = CURVE_A_neg, bcurve = CURVE_B_neg)
  }
  
  # First round is always forced to guess
  ml[[1]][,1] <- rep("Guess", nrow(ml[[1]])) %>%
    guesses %>%
    outcome(prob = probabilities[1,])

  if (strategy == "positivist") {
    # Windows
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var + 1
      if (j < 1) {j <- 1}
      # Determine next choice 
      ml[[1]][, i + 1] <- strat_positivist(ml[[1]][, j:i]) %>%
        guesses %>%
        outcome(prob = probabilities[i,])
    }
  } else if (strategy == "constructivist") {
    # Constructivist
    for (i in 1:ncol(ml[[1]])) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var + 1
      if (j < 1) {j <- 1}
      # Determine next choice
      output <- strat_constr(cbind(ml[[1]][, j:i],
                                   ml[[2]][, j:i]))
      # Experienced
      ml[[1]][, i + 1] <- output[, 1] %>%
        unlist %>%
        guesses %>%
        outcome(prob = probabilities[i,])
      # Constructed
      ml[[2]][, i + 1] <- output[, 2] %>%
        unlist %>%
        guesses %>%
        outcome(prob = probabilities[i,])
    }
  } else if (strategy == "omniscient") {
    # Omniscient
    # Determine best choice
    if (strat_var == "positive") {
      best_choice <- tibble(acurve = CURVE_A_pos, bcurve = CURVE_B_pos)
    } else if (strat_var == "neutral") {
      best_choice <- tibble(acurve = CURVE_A_neu, bcurve = CURVE_B_neu)
    } else {
      best_choice <- tibble(acurve = CURVE_A_neg, bcurve = CURVE_B_neg)
    }
    best_choice %<>%
      transmute(best = ifelse(acurve > bcurve, "A", ifelse(acurve == bcurve, "Guess", "B"))) %>% unlist
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      ml[[1]][, i + 1] <- strat_omni(dim(ml[[1]]), best_choice) %>%
        outcome(prob = probabilities[i,])
    }
  } else if (strategy == "guessing") {
    # Guessing
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      ml[[1]][, i + 1] <- strat_guessing(nrow(ml[[1]])) %>%
        guesses %>%
        outcome(prob = probabilities[i,])
    }
  } else {
    warning("Please specify a strategy to be used!")
  }
  
  # Return
  ml[[1]]
}
```

#### The simulation handler with guesses:

This function runs the simulation and returns the expected choices as well as the trials guessed. Returns a list.
```{r Simulation Guess Handler, eval=FALSE}
# Version two. Mainly identical but keeps tracks of number of guesses. Slightly less readable.
sim_handler_guesses <- function(strategy, environment, strat_var = NA, size) {
  # List to store expected choices
  df_sim <- matrix(nrow = size[1], ncol = size[2]) %>%
    as_tibble()
  no_of_guesses_constr <- no_of_guesses_exp <- df_const <- df_sim
  ml <- list(df_sim, df_const, no_of_guesses_exp, no_of_guesses_constr)
  rm(df_sim, df_const, no_of_guesses_exp, no_of_guesses_constr)
  # Determine best choice
  if (environment == "positive") {
    probabilities <- tibble(acurve = CURVE_A_pos, bcurve = CURVE_B_pos)
  } else if (environment == "neutral") {
    probabilities <- tibble(acurve = CURVE_A_neu, bcurve = CURVE_B_neu)
  } else {
    probabilities <- tibble(acurve = CURVE_A_neg, bcurve = CURVE_B_neg)
  }
  
  # First round is always forced to guess
  ml[[1]][,1] <- rep("Guess", nrow(ml[[1]])) %>%
    guesses %>%
    outcome(prob = probabilities[1,])
  
  if (strategy == "positivist") {
    # Windows
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var + 1
      if (j < 1) {j <- 1}
      # Determine next choice
      output <- strat_positivist(ml[[1]][, j:i])
      ml[[3]][which(output == "Guess"), i + 1] <- 1
      output <- guesses(unlist(output))
      ml[[1]][, i + 1] <- output %>%
        unlist() %>%
        guesses() %>%
        outcome(., prob = probabilities[i,])
    }
  } else if (strategy == "constructivist") {
    # Constructivist
    for (i in 1:ncol(ml[[1]])) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var + 1
      if (j < 1) {j <- 1}
      # Determine next choice
      output <- strat_constr(cbind(ml[[1]][, j:i],
                                   ml[[2]][, j:i]))
      # Add guesses to counter
      ml[[3]][which(output[, 1] == "Guess"), i + 1] <- 1
      ml[[4]][which(output[, 2] == "Guess"), i + 1] <- 1
      # Resolve guesses
      output[, 1] <- guesses(unlist(output[, 1]))
      # Commented out as constructed expectations do not get their guesses resolved
      # ml[[2]][, i + 1] <- guesses(unlist(ml[[2]][, i + 1]))
      
      # Update memory
      ml[[1]][, i + 1] <- outcome(unlist(output[, 1]), prob = probabilities[i,])
      ml[[2]][, i + 1] <- output[,2]
    }
  } else if (strategy == "omniscient") {
    # Omniscient
    # Determine best choice
    if (strat_var == "positive") {
      best_choice <- tibble(acurve = CURVE_A_pos, bcurve = CURVE_B_pos)
    } else if (strat_var == "neutral") {
      best_choice <- tibble(acurve = CURVE_A_neu, bcurve = CURVE_B_neu)
    } else {
      best_choice <- tibble(acurve = CURVE_A_neg, bcurve = CURVE_B_neg)
    }
    best_choice %<>%
      transmute(best = ifelse(acurve > bcurve, "A", ifelse(acurve == bcurve, "Guess", "B"))) %>% unlist
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      ml[[1]][, i + 1] <- strat_omni(dim(ml[[1]]), best_choice) %>%
        outcome(prob = probabilities[i,])
    }
  } else if (strategy == "guessing") {
    # Guessing
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      ml[[1]][, i + 1] <- strat_guessing(nrow(ml[[1]])) %>%
        guesses %>%
        outcome(prob = probabilities[i,])
    }
  } else {
    warning("Please specify a strategy to be used!")
  }
  
  ml
}
```

#### The matching handler:

This function determines expected choices based on given data.
```{r Matching Handler, eval=FALSE}
match_handler <- function(ml, strategy, strat_var = NA) {
  dfexpectations <- matrix(nrow = nrow(ml[[1]]), ncol = ncol(ml[[1]])) %>%
    as_tibble() # Tibble to store expected choices
  if (strategy == "positivist") {
    # Windows
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var
      if (j < 1) {j <- 1}
      # Determine expected choices 
      dfexpectations[, i + 1] <- strat_positivist(ml[[1]][, j:i])
    }
  } else if (strategy == "constructivist") {
    # Constructivist
    df_constructed <- dfexpectations
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      # Define lower window boundary
      j <- i - strat_var
      if (j < 1) {j <- 1}
      # Determine expected choices 
      output <- strat_constr(cbind(ml[[1]][, j:i],
                                   ml[[2]][, j:i]))
      dfexpectations[, i + 1] <- output[,1]
      df_constructed[, i + 1] <- output[,2]
    }
  } else if (strategy == "omniscient") {
    # Omniscient
    # Determine best choice
    if (strat_var == "positive") {
      best_choice <- tibble(acurve = CURVE_A_pos, bcurve = CURVE_B_pos)
    } else if (strat_var == "neutral") {
      best_choice <- tibble(acurve = CURVE_A_neu, bcurve = CURVE_B_neu)
    } else {
      best_choice <- tibble(acurve = CURVE_A_neg, bcurve = CURVE_B_neg)
    }
    best_choice %<>%
      transmute(best = ifelse(acurve > bcurve, "A", ifelse(acurve == bcurve, "Guess", "B"))) %>% unlist
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      dfexpectations[, i + 1] <- strat_omni(dim(ml[[1]][1:i]), best_choice)
    }
  } else if (strategy == "guessing") {
    # Guessing
    for (i in 1:(ncol(ml[[1]]) - 1)) { # Iterate over strategy
      dfexpectations[, i + 1] <- strat_guessing(nrow(ml[[1]]))
    }
  } else {
    warning("Please specify a strategy to be used!")
  }
  
  dfexpectations
}
```

And then this function determines the matches
```{r Matcher, eval=FALSE}
matching <- function(experienced, expected) {
  matches <- matrix(nrow = nrow(expected), ncol = ncol(expected)) %>%
    as_tibble()
  
  
  for (i in 2:ncol(expected)) {
    matches[experienced[, i] %>%
              unlist() %>%
              substr(., 2, 2) == expected[, i], i] <- 1
  }
  
  matches %>%
    rowSums(na.rm = TRUE)
}
```

### Strategies {.tabset .tabset-fade}

We compare four strategies, two defined by Juslin and colleagues and two normative strategies. The strategies are:  
 * A **Positivist** strategy: no constructed memory for the not-chosen option  
 * A **Constructivist** strategy: as the name suggests, outcomes for the not-chosen option are constructed  
 * **Guessing**: guess on every trial  
 * An **Omniscient** strategy: knows the distribution of outcome probabilities and always chooses the one with higher outcome probability

The positivist and constructivist strategies are both based on windows of varying size.

#### Windows
```{r Positivist, eval=FALSE}
### Windows
strat_positivist <- function(dfpositivist) {
  # Determine expected next choice
  expected <- apply(dfpositivist, 1, windowchoice)
  
  # return expectations
  expected
}
```

#### Constructivist Coding
```{r Constructivist, eval=FALSE}
### Constructivist
strat_constr <- function(dfconstr) {
  # Determine expected next choice
  expected <- apply(dfconstr, 1, windowchoice, TRUE)
  
  # Tease apart
  expected <- str_split_fixed(expected, "-", 2) %>%
    as_tibble %>%
    mutate(V2 = ifelse(V2 == "", "Guess", V2))
  
  # return expectations
  expected
}
```

#### Omniscient
```{r Omniscient, eval=FALSE}
strat_omni <- function(dfomni, best) {
 rep(best[dfomni[2]], dfomni[1])
}
```

#### Guessing
```{r Guessing, eval=FALSE}
### Guessing
strat_guessing <- function(dfguess) {
  # Fill with guesses and return
  rep("Guess", dfguess)
}
```




## Simulations {.tabset .tabset-fade}

### Most successful strategy {.tabset .tabset-fade}

```{r sim_load, include=FALSE}
load(here("Output/sim_results.RData"))
sim_length <- nrow(success_results)
```

First, which strategy is most successful? We ran `r sim_length` iterations of the simulation.

```{r sim_descriptive, echo=FALSE}
# Descriptive
success_results %>%
  group_by(strategy, environment) %>%
  summarize(max = max(success),
            avg = mean(success),
            min = min(success)) %>%
  knitr::kable(caption = "Descriptive statistics") %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

#### Static
```{r sim_graph_static, echo=FALSE}
# Descriptive
success_results %>%
  ggplot(aes(x = window,
             y = success,
             shape = environment,
             color = strategy)) +
  geom_point() +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()
```

#### Dynamic
```{r sim_graph_dynamic, echo=FALSE}
# Descriptive
p <- success_results %>%
  ggplot(aes(x = window,
             y = success,
             shape = environment,
             color = strategy)) +
  geom_point() +
  scale_color_brewer(palette = "Dark2") +
  theme_minimal()
ggplotly(p)
```

## Paper

### Theory
Much about our surrounding environment follows cyclic patterns. As the earth orbits the sun, day and night alternate while seasons come and go. These largescale patterns then dictate patterns in our lives: We tend to structure our awake time around day and night times and we tend to engage in different activities depending on the time of the year. For many, the seasons influence the available foods and for many workers (e.g. farmers) the seasons prescribe the type of work currently to be done. Cyclic patterns are everywhere in life.  

However, the current decision making literature does not seem to represent this supposition adequately. Most paradigms that involve decisions between two or more options have either static outcome probabilities or include but a single change (gradual or abrupt) <citations>. Only few studies include cyclic variations in the outcome probabilities (e.g. Bott & Heit, 2004). This not only limits the external validity of studies but, far more fundamentally, affects the decision strategies to be invested. For example, probability matching becomes a powerful, adaptive strategy once there are patterns to be detected (Gaissmeier, xxx) while at the same time its precise definition in a cyclic environment becomes unclear. And foraging theories need to account for continuous exploration, or at the least flexibility during exploitation phases as maximizing alone will not be an adaptive behavior.  

Here, we create a two-armed bandit task with continuously, sinusoidally interweaving outcome probabilities and simulate three decision making strategies (decision windows, recency weighting, and constructivist coding) as well as two normative strategies (guessing and omniscient). We then have participants complete the bandit task and match these strategies to their behavior. The two normativce strategies serve as benchmarks for behavior.

### Strategies 
Two- or multi-armed bandit tasks have become somewhat of a gold standard in the decision making literature. They allow for a controlled environment in which to analyse participants' behavior and then match their behavior to predictions made by decision strategies.  

(...)  

Three such families of strategies we will investigate closer.

#### Windows

Kareev (1995, 1997) argues that small samples hava an advantage in detecting correlation due to the stronger skew of the covariation the smaller the sample is. This proposition was quickly picked up by others. For example, Hertwig and Todd (2005) and Kareev (2000) argue that cognitive limitations are, in fact, adaptive as they allow for quicker learning of contingencies. Furthermore, the cognitive limitations make it implausible that humans can always keep track of the full outcome history in order to determine the next choice. Instead, it is a reasonable assumption that only the last few trials, a recent historic window, are used to determine the next choice (Otto et al., 2011).  

#### Constructivist Coding

Until now, all strategies assumed that the decision maker receives feedback on every trial and ignores non-feedback trials (such as the option not chosen). Costructivist Coding, however, proposes that in the absense of feedback, decision makers memorize the expected outcome. Future decisions will then be based not only on experienced outcomes but also on constructed outcomes where necessary (Elwin, Juslin, Olsson, & Enkvist, 2007; Ghaffarzadegan & Stewart, 2011; Henriksson, Elwin, & Juslin, 2010). In bandit tasks in which the decision maker only receives feedback for the chosen outcome, an outcome for the alternative option might be constructed for every single trial.  

### Methods 

#### Simulations
Part I: Simulation of strategies. Performance. Which strategies perform best. Why?  

#### Experiment
Part II: Matching to participant data. What do participants seem to do?

### Results
Which strategies perform best and why, what do people seem to do.

### Discussion
Match or discrepancy of simulation and experiment?
